\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[left=4.0cm, right=4.0cm]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz-cd}
\usepackage{ytableau}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\E}{\mathbb{E}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\f}[1]{\text{#1}}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\renewcommand{\^}{\wedge}
\renewcommand{\v}{\vee}


\pagestyle{fancy}
\fancyhf{}
\lhead{\today}
\chead{CS 70}
\rhead{William Wang}
\cfoot{\thepage}

\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% \setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\title{\textbf{CS 70}}
\author{\large Taught by Hulett, Yang\\
Homework 0 by William Wang}
\date{June 24, 2019}

\begin{document}

\maketitle

\newpage

Sundry: I worked on this homework by myself.
\begin{enumerate}
    \item 
        \begin{enumerate}
            \item Website url: https://www.eecs70.org/
            \item \underline{Grade Breakdown:}
                \begin{enumerate}
                    \item Midterm 1: 22\%
                    \item Midterm 2: 22\%
                    \item Final: 45\%
                    \item Sundry: 1\%
                    \item Homework: 10\%
                \end{enumerate}
        \end{enumerate}
    \item 
        \begin{enumerate}
            \item Yes. All homework submissions must be written by the student.
            \item No. Sharing approaches is permitted and notes help with identifying the correct approach without just giving a solution.
            \item No. External sources are okay to use as long as the student understands the solution and doesn't just copy the solution. Also the student credits the source.
            \item Yes. Solutions should never be shared between students.
            \item Yes. Solutions should never be shared between students.
        \end{enumerate}
    \item
        \begin{enumerate}
            \item Note 0 (@45)
            \item The question is too broad and difficult to explain in a piazza post. A better question for piazza would be to ask a specific question about a specific section of the proof.
        \end{enumerate}
    \item
        \begin{enumerate}
            \item $\forall x \exists y \big((P(x) \^ Q(x,y)) \implies x \leq \sqrt{y}\big)$
            \item $\displaystyle \sum_{i=0}^{k}i = \frac{(k)(k+1)}{2}$
        \end{enumerate}
    \item I pledge to uphold the university’s honor code: to act with honesty, integrity, and respect for others, including their work. By signing, I ensure that all written homework I submit will be in my own words, that I will acknowledge any collaboration or help received, and that I will neither give nor receive help on any examinations.
    
    $\quad$ -William Wang
\end{enumerate}


\end{document}
