\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[left=4.0cm, right=4.0cm]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz-cd}
\usepackage{ytableau}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\E}{\mathbb{E}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\f}[1]{\text{#1}}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\renewcommand{\^}{\wedge}
\renewcommand{\v}{\vee}


\pagestyle{fancy}
\fancyhf{}
\lhead{\today}
\chead{CS 70}
\rhead{William Wang}
\cfoot{\thepage}

\makeatletter
\renewcommand{\@seccntformat}[1]{}
\makeatother

% \setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}

\title{\textbf{CS 70}}
\author{\large Taught by Hulett, Yang\\
Homework 4 by William Wang}
\date{July 21, 2019}

\begin{document}

\maketitle
\newpage
Sundry: I worked on this homework by myself.\\
\begin{enumerate}
    \item
        \begin{enumerate}
            \item There's clearly a number that cannot be described with 100 characters since 100 characters gives a finite bound. There are only 67 characters in the sentence, which means that it is not the smallest positive integer not definable in under 100 character, but it also is.
            \item For any n-bit string, there are $2^n$ possible representations. For unique numbers, there are only $2^n - 1$ many choices to compress it to, which means that there must be one that cannot be compressed.
            \item P takes in n, converts it into an integer using a while look and repeatedly dividing by powers of 2. Feed the bit string into K and keep track of the complexity. If the complexity is greater than the previous max, then replace the current max. If equal do nothing. Return max.
            \item There is at least 1 incompressible string for every value $\leq n$. This incompressible string has a complexity $\geq n$. If $n > m$ then the incompressible string must be also greater than m and cannot be represented in m bits.
        \end{enumerate}
    \item 
        \begin{enumerate}
            \item 8!
            \item $3^8 * 8!$
            \item $3^8 * 8! / 3 = 3^7 * 8!$
            \item part c divided by 6 different top faces and 4 rotations that lead to the same orientations = $3^7 * 8!/(6*4)$
            \item valid corner positioning stays the same, while there are $12! * 2^12$ new possible orientations per orientation of corner pieces = $3^12 * 3^8 * 12! * 8!$
        \end{enumerate}
    \item  
        \begin{enumerate}
            \item treat "COME" as a single 'letter'. Then there are 4! ways to contain a substring of "COME". For a subsequence, fix the other letters in position and for any choice of putting the letters of "COME" into the sequence, there is only 1 that results in a valid subsequence. Then there are ${7 \choose 4}$ ways to put "COME" in, and 3! ways to rearrange "S, T, U". So there are ${7 \choose 4} * 3!$ choices.
            \item 50 for 2, 33 for 3, 20 for 5\\
            16 for 6, 10 for 10, 6 for 15\\
            3 for 30\\
            Total = (50 + 33 + 20) - (16 + 10 + 6) + 3 = 74
            \item fix $x_0. x_0$ must be between 0 and 90. There are $46 \choose 3$ ways to choose $x_1 - x_4$ for $x_0  = 0$. There are $45 \choose 3$ ways to choose for $x_0 = 5$... There are a total of ${3 \choose 3} + {4\choose 3} + ... + {46 \choose 3}$ ways = ${47 \choose 4}$.
            \item For any choice of numbers, there is only 1 valid orientation. Then we have 7 items and 9 dividers where each 'slot' is a different number between 0 and 9 = ${16 \choose 9}$. 
        \end{enumerate}
    \item
        \begin{enumerate}
            \item ${n \choose k}$
            \item $x^k * y^{n-k}$
            \item ${n \choose k} * [x^k * y^{n-k} - (kx + (n-k)y)]$
            \item The total profit of making every unique keychain of exactly $k$ blue beads is equal to the cost of making it raised to the $n$ power???
        \end{enumerate}
    \item
        \begin{enumerate}
            \item $[18! / (6! * 8! * 3!)] / [22! / (5! * 8! * 6! * 3!)] = 1/1463$
            \item $2^8 / 3^8$
            \item $15^5 / 20^ 5$
        \end{enumerate}
    \item
        Yes. By the same logic as the Monty Hall Problem, there's a lower chance that my friend shoots a bullet if I respin the revolver.
    \item
        \begin{enumerate}
            \item $2^n$
            \item $1/(2^n)$
            \item Probability = ${n \choose k} * 1/k - {n \choose k+1} * 1/(k+1) + ...$ For $k \geq 4logn + 1$, each negative term can at least cancel out the positive term? resulting in a final term of 1/n??
        \end{enumerate}
\end{enumerate}
\end{document}